### 2018-08-06 Sections/optical_encoding_of_quantum_information.tex
floats
Formulas for TEM modes

\begin{figure}[!htb]
\includegraphics[width=0.15\textwidth]{photonic_qubit_encodings}
\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{pol_to_dual_conversion}
\caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\caption{The family of Hermite functions, $H_n(x)$, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}

@@

Of particular interest are transverse electro-magnetic (TEM) modes, which are the two-dimensional eigenfunctions of the electro-magnetic field in the transverse direction of a light field. These are given by modulations of Hermite or Laguerre polynomials\index{Laguerre polynomials}, depending on the geometry of the medium through which the light is propagating (e.g optical fibre, free-space, wave-guides), which effectively impose boundary conditions on the electro-magnetic field.

The TEM modes are discrete, and denoted TEM$_{mn}$, where \mbox{$m,n\in \mathbb{Z}_+$}. TEM modes can be prepared and manipulated using holograms\index{Holograms}. Examples are shown in Fig.~\ref{fig:TEM_modes}.

\begin{figure*}[!htb]
\includegraphics[width=0.49\textwidth]{TEM_cylinder}
\includegraphics[width=0.49\textwidth]{TEM_rectangular}
\caption{TEM$_{mn}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic modes}\label{fig:TEM_modes}
\end{figure*}

@@

\begin{figure}[!htb]
\includegraphics[width=0.25\textwidth]{time_bin_encoding}
\caption{Time-bin encoding on an $n$-level quantum system. Time-bin are temporally localised with envelopes $\xi_j$, orthogonal to all others, different only via temporal displacements. The temporal separation between each consecutive time-bin is given by $\tau$.}\label{fig:time_bin_encoding}	
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{coherent_state_encoding}
\caption{Phase-space representation of a coherent state with complex amplitudes $\pm\alpha$. For sufficiently large amplitude one can approximate orthogonality, enabling a qubit encoding.} \label{fig:coherent_state_encoding}	
\end{figure}

>>>>

\begin{figure}[htpb]
\includegraphics[width=0.15\textwidth]{photonic_qubit_encodings}
\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.3\textwidth]{pol_to_dual_conversion}
\caption{Conversion from single-photon polarisation encoding to dual-rail encoding, using a polarising beamsplitter (PBS) and wave-plate (WP). The PBS separates the polarisation components into two distinct spatial modes. The WP then rotates the polarisation of one of the spatial modes such that it has the same polarisation as the other. Conversion from dual-rail to polarisation encoding is just the reverse of this procedure.} \label{fig:pol_to_dual_conv}\index{Polarising beamsplitters}
\end{figure}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.475\textwidth]{hermite_basis}
	\caption{The family of Hermite functions, $H_n(x)$, are an example of an orthonormal basis of continuous functions that could be utilised in the spatio-temporal encoding of qudits into photonic wave-packets. Shown here are \mbox{$n=0,1,2,3$}.}\index{Hermite functions}\label{fig:hermite_basis}
\end{figure}

@@

Of particular interest are transverse electro-magnetic (TEM) modes, which are the two-dimensional eigenfunctions of the electro-magnetic field in the transverse direction of a light field. The are obtained by imposing boundary conditions on the electro-magnetic field, depending on the medium the geometry of the medium (e.g optical fibre, free-space, wave-guides).

Specifically, for cylindrical and rectangular boundary conditions, the intensity profile of the TEM modes are given by,
\begin{widetext}
\begin{align*}
	I_{p,l}^{\mathrm{cyl}}(\rho,\varphi) &= I_0 \rho^l L_p^l(\rho)^2 \cos(l\varphi)e^{-\rho},\nonumber\\
	I_{m,n}^{\mathrm{rect}}(x,y,z) &= I_0\left(\frac{\omega_0}{\omega}\right)^2 \left[H_m\left(\frac{\sqrt{2}x}{\omega}\right)e^{-\frac{x^2}{\omega^2}}\right]^2 \left[H_n\left(\frac{\sqrt{2}y}{\omega}\right)e^{-\frac{y^2}{\omega^2}}\right]^2,
\end{align*}
\end{widetext}
where,
\begin{align}
	H_n(x) &= n! \sum_{m=0}^{\lfloor \frac{n}{2}\rfloor} \frac{(-1)^m}{m!(n-2m)!} (2x)^{n-2m},\nonumber\\
	L_n(x) &= \sum_{k=0}^n \binom{n}{k} \frac{(-1)^k}{k!}x^k,
\end{align}
are the Hermite and Laguerre polynomials\index{Hermite polynomials}\index{Laguerre polynomials} respectively. These examples are shown in Fig.~\ref{fig:TEM_modes}.

\begin{figure*}[htpb]
\includegraphics[width=0.49\textwidth]{TEM_cylinder}
\includegraphics[width=0.49\textwidth]{TEM_rectangular}
\caption{TEM$_{mn}$ modes for cylindrical (left) and rectangular (right) mode profiles.}\index{Transverse electro-magnetic modes}\label{fig:TEM_modes}
\end{figure*}

The TEM modes are discrete, and denoted TEM$_{mn}$, where \mbox{$m,n\in \mathbb{Z}_+$}. TEM modes can be prepared and manipulated using holograms\index{Holograms} in the form of phase-masks.

@@

\begin{figure}[htpb]
\includegraphics[width=0.25\textwidth]{time_bin_encoding}
\caption{Time-bin encoding on an $n$-level quantum system. Time-bin are temporally localised with envelopes $\xi_j$, orthogonal to all others, different only via temporal displacements. The temporal separation between each consecutive time-bin is given by $\tau$.}\label{fig:time_bin_encoding}	
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{coherent_state_encoding}
\caption{Phase-space representation of a coherent state with complex amplitudes $\pm\alpha$. For sufficiently large amplitude one can approximate orthogonality, enabling a qubit encoding.} \label{fig:coherent_state_encoding}	
\end{figure}
